\chapter*{\uppercase{ACKNOWLEDGEMENT}}
\addcontentsline{toc}{section}{\bfseries \uppercase{Acknowledgement}}
\begin{spacing}{1.5}
\begin{sloppypar}
It is my privilege to express my deepest sense of gratitude and sincere
thanks to {\textbf{Dr. M. VIJAYALAKSHMI,}} Professor, Project Guide, Department of Information Science and Technology, College of Engineering, Guindy, Anna University, for her constant supervision, encouragement, and support in my project work. I greatly appreciate the constructive advice and motivation that was given to help me advance my project in the right direction.

I am grateful to {\textbf{Dr. S. SWAMYNATHAN,}} Professor and Head, Department
of Information Science and Technology, College of Engineering Guindy, Anna University for providing us with the opportunity and necessary resources to do this project.

I would also wish to express my deepest sense of gratitude to the
Members of the Project Review Committee: {\textbf{Dr. J. INDUMATHI,}} Professor, {\textbf{Dr. SELVI RAVINDRAN,}} Associate Professor, {\textbf{Dr. D. NARASHIMAN,}} Teaching Fellow Department of Information Science and Technology,College of Engineering Guindy, Anna University, for their guidance and useful suggestions that were beneficial in helping me improve my project.

I also thank the faculty member and non teaching staff members of the Department of Information Science and Technology, Anna University, Chennai for their valuable support throughout the course of our project work.
\begin{flushright}
 {\textbf{JIVITESH NARAYAN}}\\
 {\textbf{(2022176030)}} 
\end{flushright}

                                                     
\end{sloppypar}
\end{spacing}